Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-12-12 parts/example.tex
add sets of actions

The actions of the original model make $3$ classes of priorities, as represented in \pref{fig:metazoan-php}.
Thus, although the actions of the highest class of priority are only used to update a cooperative sort,
the actions of the two other classes of priorities do have a biological meaning.
%by representing different reaction rates.
Indeed, they have been derived given the different reaction rates,
given the fact that the switches of genes $a$ and $c$ have to alternate in order not to miss a stripe.

\begin{figure}[htp]
  \centering
  \scalebox{1}{
  \begin{tikzpicture}
    \TSort{(0,4)}{c}{2}{l}
    \TSort{(1,1)}{f}{2}{l}
    \TSort{(6,4)}{a}{2}{r}

@@

\pref{fig:metazoan-ph} gives the flattening of this model.
It contains $2$ classes of priority, and prioritised actions are only used to update cooperative sorts.
Note that according to the simplifications mentioned at the end of \pref{ssec:flattening},
the auto-action $h_1 = \PHhit{c_1}{c_1}{c_0}$ in $\oPH$ has been flattened to a regular action $\PHhit{a_0}{c_1}{c_0}$
because its playability property could be simplified to $\Fop{h_1} \equiv c_1 \wedge a_0 \equiv a_0$.

@@

\begin{figure}[htp]
  \centering
  \scalebox{1}{
  \begin{tikzpicture}
    \TSort{(-5,4)}{c}{2}{l}
    \TSort{(0,1)}{f}{2}{l}
    \TSort{(5,4)}{a}{2}{r}

@@

>>>>

The actions of the original model make $3$ classes of priorities, as represented in \pref{fig:metazoan-php}
and listed in \pref{tab:metazoan-php-actions}.
Thus, although the actions of the highest class of priority are only used to update a cooperative sort,
the actions of the two other classes of priorities do have a biological meaning.
%by representing different reaction rates.
Indeed, they have been derived given the different reaction rates,
given the fact that the switches of genes $a$ and $c$ have to alternate in order not to miss a stripe.

\begin{figure}[p]
  \centering
  \scalebox{1}{
  \begin{tikzpicture}
    \TSort{(0,4)}{c}{2}{l}
    \TSort{(1,1)}{f}{2}{l}
    \TSort{(6,4)}{a}{2}{r}

@@

\begin{table}[p]
\modMF{
\begin{align*}
  \PHh^{(1)} = \{ \quad
    & \PHfrappe{f_1}{fc_{00}}{fc_{10}} \quad , \quad
    \PHfrappe{f_1}{fc_{01}}{fc_{11}} \quad , \\
    & \PHfrappe{f_0}{fc_{10}}{fc_{00}} \quad , \quad
    \PHfrappe{f_0}{fc_{11}}{fc_{01}} \quad , \\
    & \PHfrappe{c_1}{fc_{00}}{fc_{01}} \quad , \quad
    \PHfrappe{c_1}{fc_{10}}{fc_{11}} \quad , \\
    & \PHfrappe{c_0}{fc_{01}}{fc_{00}} \quad , \quad
    \PHfrappe{c_0}{fc_{11}}{fc_{10}}
  \quad \} \\
  \PHh^{(2)} = \{ \quad
    & \PHfrappe{c_1}{a_1}{a_0} \quad , \quad
    \PHfrappe{fc_{10}}{a_0}{a_1}
  \quad \} \\
  \PHh^{(3)} = \{ \quad
    & \PHfrappe{c_1}{c_1}{c_0} \quad , \quad
    \PHfrappe{f_1}{c_0}{c_1}
  \quad \} \\
\end{align*}%
}%
  \caption{\label{tab:metazoan-php-actions}%
    Sets of actions of the metazoan segmentation model depicted
    in \pref{fig:metazoan-php}.
  }
\end{table}

\pref{fig:metazoan-ph} gives the flattening of this model,
\modMF{
whose actions are detailed in \pref{tab:metazoan-ph-actions}.
}%
It contains $2$ classes of priority, and prioritised actions are only used to update cooperative sorts.
Note that according to the simplifications mentioned at the end of \pref{ssec:flattening},
the auto-action $h_1 = \PHhit{c_1}{c_1}{c_0}$ in $\oPH$ has been flattened to a regular action $\PHhit{a_0}{c_1}{c_0}$
because its playability property could be simplified to $\Fop{h_1} \equiv c_1 \wedge a_0 \equiv a_0$.

@@

\begin{figure}[p]
  \centering
  \scalebox{1}{
  \begin{tikzpicture}
    \TSort{(-5,4)}{c}{2}{l}
    \TSort{(0,1)}{f}{2}{l}
    \TSort{(5,4)}{a}{2}{r}

@@

\begin{table}[p]
\modMF{
\begin{align*}
  \PHh^{(1)} = \{ \quad
    & \PHfrappe{f_1}{fc_{00}}{fc_{10}} \quad , \quad
    \PHfrappe{f_1}{fc_{01}}{fc_{11}} \quad , \\
    & \PHfrappe{f_0}{fc_{10}}{fc_{00}} \quad , \quad
    \PHfrappe{f_0}{fc_{11}}{fc_{01}} \quad , \\
    & \PHfrappe{c_1}{fc_{00}}{fc_{01}} \quad , \quad
    \PHfrappe{c_1}{fc_{10}}{fc_{11}} \quad , \\
    & \PHfrappe{c_0}{fc_{01}}{fc_{00}} \quad , \quad
    \PHfrappe{c_0}{fc_{11}}{fc_{10}} \quad , \\
    & \PHfrappe{f_1}{fa_{00}}{fa_{10}} \quad , \quad
    \PHfrappe{f_1}{fa_{01}}{fa_{11}} \quad , \\
    & \PHfrappe{f_0}{fa_{10}}{fa_{00}} \quad , \quad
    \PHfrappe{f_0}{fa_{11}}{fa_{01}} \quad , \\
    & \PHfrappe{a_1}{fa_{00}}{fa_{01}} \quad , \quad
    \PHfrappe{a_1}{fa_{10}}{fa_{11}} \quad , \\
    & \PHfrappe{a_0}{fa_{01}}{fa_{00}} \quad , \quad
    \PHfrappe{a_0}{fa_{11}}{fa_{10}}
  \quad \} \\
  \PHh^{(2)} = \{ \quad
    & \PHfrappe{c_1}{a_1}{a_0} \quad , \quad
    \PHfrappe{fc_{10}}{a_0}{a_1} \quad , \\
    & \PHfrappe{a_0}{c_1}{c_0} \quad , \quad
    \PHfrappe{fa_{11}}{c_0}{c_1}
  \quad \}
\end{align*}%
}%
  \caption{\label{tab:metazoan-ph-actions}%
    Sets of actions of the flattened metazoan segmentation model depicted
    in \pref{fig:metazoan-ph}.
  }
\end{table}
